\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-10-26 demystify.tex
Updates from Overleaf

After you submit your PhD application (usually in December), it will be first screened
for general requirements, e.g., did you submit your transcripts and standard scores? did your reference writers submit their letters?

@@

\subsubsection{Tenured, Tenure Track, Teaching,  Assistant Profs., Associate Profs}
There are several types of faculty in a university that has a CS PhD program. For example, you might hear about tenured,  tenure track, teaching faculty.  You might also see assistant, associate, full, adjunct, emeritus, teaching, research professors. Here is a primer on these titles.  Note that these are general and might not apply to all universities.

@@

@@

\paragraph{History} This document was conceived during a lunch with Craig Yu at GMU.  We talked on about why GMU were not able to attract good Vietnamese and other international students, despite having a much stronger CS program than many schools that these students want to go to (part of the reason is described in \S\ref{sec:ranking}) and wished there were a way for international students to know about the US PhD programs (as well as for US faculty to understand more about international students and therefore have better chance of recruiting and working with them). I was also  a member of the large VietPhD group on Facebook and saw many questions from students about PhD programs.  However, most active participant are students in non-CS fields or not in US. Like ChatGPT, their answers to CS PhD program in the US could be informative and helpful, but unfortunately not always accurate and sometimes leading to more confusion. So I thought it would be useful to have a document that is specific to CS PhD programs in the US from an insider prospective.

>>>>

After you submit your PhD application (usually December 15), it will be first screened
for general requirements, e.g., did you submit your transcripts and standard scores? did your reference writers submit their letters?

@@

\subsubsection{Tenured, Tenure Track, Teaching,  Assistant Profs., Associate Profs}
There are several types of faculty in a university that has a CS PhD program.  You might hear about tenured,  tenure track, teaching faculty.  You might also see assistant, associate, full, adjunct, emeritus, teaching, research professors. Here is a primer on these titles.

@@

% \section{Additional Resources}
% \begin{itemize}
% \item \bibentry{nlpphd}
% \end{itemize}

@@

\paragraph{History} This document was conceived during a lunch with Craig Yu at GMU.  We talked on about why GMU were not able to attract good Vietnamese and other international students, despite having a much stronger CS program than many schools that these students want to go to (part of the reason is described in \S\ref{sec:ranking}). We wished there were a way for international students to know about the US PhD programs (as well as for US faculty to understand more about international students and therefore have better chance of recruiting and working with them). I was also  a member of the large VietPhD group on Facebook and saw many questions from students about PhD programs.  However, most active participant are students in non-CS fields or not in US. Like ChatGPT, their answers to CS PhD program in the US could be informative and helpful, but unfortunately not always accurate and sometimes leading to more confusion. So I thought it would be useful to have a document that is specific to CS PhD programs in the US from an insider prospective.
